Bioverse: The Habitable Zone Inner Edge Discontinuity as an Imprint of Runaway Greenhouse Climates on Exoplanet Demographics

### 2023-04-22 src/tex/ms.tex

In particular, we test the capability of the \plato\ \citep[PLAnetary Transits and Oscillation of stars, ][]{Rauer2016} mission, which will measure the radii of a large number of terrestrial-sized planets, to detect the radius/density discontinuity and determine its sensitivity to model assumptions and fundamental processes.
We then perform a parameter study to explore which trades in the survey design of a \plato-like mission maximizes its diagnostic power to test runaway greenhouse climate models through the detection of the habitable zone inner edge discontinuity.

@@

\section*{Data Availability}
All data sets and software required to reproduce our results and this article are available through GitHub and Zenodo.
The code to reproduce the figures can be accessed via the icon links associated with the respective figure caption.

>>>>

In particular, we test the capability of the \plato\ \citep[PLAnetary Transits and Oscillation of stars, ][]{Rauer2016} mission, which will measure the radii of a large number of terrestrial-sized planets, to detect the radius/density discontinuity and determine its sensitivity to model assumptions and fundamental processes.
We then perform a parameter study to explore which trades in the survey design of a \plato-like mission maximize its diagnostic power to test runaway greenhouse climate models through the detection of the habitable zone inner edge discontinuity.

@@

%\section*{Data Availability}
\section*{Reproducibility}
%All data sets and software required to reproduce our results and this article are available through GitHub and Zenodo.
This study uses the reproducibility framework ``showyourwork''~\citep{Luger2021}.
All code required to reproduce our results, figures, and this article itself is available at \url{https://github.com/matiscke/magmaocean}.
The code to reproduce a figure can be accessed via the icon link next to the respective figure caption.
